Meta RL analyses

### 2019-02-08 writing/embedded_meta_learning.tex
Framing

\section{Introduction}
Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep{Lake2017}. One fundamental reason for this is the separation of knowledge within deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between these. That is, neural networks knowledge about \textbf{what} is being computed is \textbf{inaccessible} by the computations. By contrast, humans are frequently consciously aware of both our representations of input, the things we can do with them, and the relationships between data and tasks. This is true for domains from game playing to natural language understanding. \par
One of the abilities that this grants humans is rapid adaptation of our behavior. The problem of rapid learning has been partially addressed by meta-learning systems \citep{}. However, humans can take rapidly acquired knowledge and flexibly alter their behavior in accordance with a change in task demands or a single instruction. For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance \textbf{without any retraining} (i.e. zero-shot). Deep learning systems at present lack this representational flexiblity. \par
In this paper, we propose a new class of architectures which essentially take a \textbf{functional perspective} on meta-learning. By treating both data and tasks as functions, we can conceptually think of both data \textbf{and} learned functions as transformable. This yields the ability to not only learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing task demands. We suggest that this ability will be key to building more intelligent and flexible deep learning systems. \par
In particular, we propose a meta-learning architecture which embeds data (including natural language inputs) and tasks in a shared space, and meta-learns to execute mappings over this space. We demonstrate the greater flexibility of this approach.
\section{Method}
\subsection{Architecture}
\begin{figure}
\centering
\begin{tikzpicture}[auto]

@@

\subsection{Operation}
A basic forward pass through the system might look as follows.
\begin{enumerate}
\item A training dataset of (input, target) pairs is embedded by $\mathcal{I}$ and $\mathcal{T}$ to produce a set of paired embeddings. Another set of (possibly unlabeled) inputs is provided and embedded.
\item The meta network $\mathcal{M}$ maps the set of embedded (input, target) pairs to a function embedding.
\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $f$, which is used to transform the second set of inputs to a set of output embeddings.
\item The output embeddings are decoded by $\mathcal{O}$ to produce a set of outputs.
\end{enumerate}
This system can be trained end-to-end if labels are provided for the second set of inputs. In particular, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0^*), ...\}$), and some loss function $\mathcal{L}(y^*, \hat{y})$ defined on a single target output $y^*$ and actual model output $\hat{y}$, for some input $x$. We define our total loss computed on some dataset $D_2$ as:
$$\mathbb{E}_{x\in {D}_2} \left[ \mathcal{L}\left(y^*, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]$$
where $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
$$f_{D_1} = \mathcal{H}\left(\mathcal{M}\left(\right)\right)

>>>>

\section{Introduction}
Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep{Lake2017}. One fundamental reason for this is the separation of knowledge within deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between these. That is, neural networks knowledge about \textbf{what} is being computed is \textbf{inaccessible} by the computations. By contrast, humans are frequently consciously aware of both our representations of input, the things we can do with them, and the relationships between data and tasks. This is true for domains from game playing to natural language understanding. \par
One of the abilities that this grants humans is rapid adaptation of our behavior. The problem of rapid learning has been partially addressed by meta-learning systems \citep{}. However, humans can take rapidly acquired knowledge and flexibly alter their behavior in accordance with a change in task demands or a single instruction. For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance \textbf{without any retraining} (i.e. zero-shot). Deep learning systems at present lack this representational flexiblity. \par
In this paper, we propose a new class of architectures which essentially take a \textbf{functional perspective} on meta-learning. By treating tasks as functions, we can conceptually think of both data \textbf{and} learned functions as transformable. This yields the ability to not only learn to solve new tasks, but to learn how to flexibly transform these solutions in response to changing task demands. We suggest that this ability will be key to building more intelligent and flexible deep learning systems. \par
In particular, we propose a meta-learning architecture which embeds data (including natural language inputs) and tasks in a shared space, and meta-learns to execute mappings over this space. We demonstrate the greater flexibility of this approach.
\section{Method}
\subsection{Architecture}
The essential idea of the architecture is that we separate the system into two parts: 
\begin{enumerate}
\item Domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$
\item A meta-learning system which:
    \begin{enumerate}
    \item Embeds tasks into the shared embedding space $Z$.
    \item Learns to perform tasks in accordance with their embeddings.
    \end{enumerate}
\end{enumerate}
The utility of having a completely shared space $Z$ in which data, language, and tasks are represented is that it allows for arbitrary mappings between these distinct types of data. In addition to basic tasks, the system could in principle learn to map language to tasks (follow instructions) or tasks to language (explaining behavior), or tasks to tasks (changing behavior). This is a step closer to the flexible reasoning humans display. \par
Without training on these mappings, of course, the system will not be able to execute them well. However, ideally if it is trained on a set of such mappings, it will be able to generalize these to new instances drawn from the same data/task distribution. For instances that fall outside its data distribution or for optimal performance it may require some retraining. This reflects the structure of human behavior -- we are able to learn rapidly when new knowledge is relateively consistent with our previous knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow. \par

\begin{figure}
\centering
\begin{tikzpicture}[auto]

@@

\subsection{Operation}
A basic forward pass through the system might look as follows.
\begin{enumerate}
\item A training dataset of (input, target) pairs is embedded by $\mathcal{I}$ and $\mathcal{T}$ to produce a set of paired embeddings. Another set of (possibly unlabeled) inputs is provided and embedded.
\item The meta network $\mathcal{M}$ maps the set of embedded (input, target) pairs to a function embedding.
\item The hyper network $\mathcal{H}$ maps the function embedding to parameters for $f$, which is used to transform the second set of inputs to a set of output embeddings.
\item The output embeddings are decoded by $\mathcal{O}$ to produce a set of outputs.
\end{enumerate}
This system can be trained end-to-end if labels are provided for the second set of inputs. In particular, suppose we have some dataset of input, target pairs ($D_1 = \{(x_0, y_0), ...\}$), and some loss function $\mathcal{L}(y, \hat{y})$ defined on a single target output $y$ and actual model output $\hat{y}$, for some input $x$. We define our total loss computed on some dataset $D_2$ as:
$$\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathcal{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]$$
where $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
$$f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_0\right), \mathcal{T}\left(y_0\right) \right), \left(\mathcal{I}\left(x_1\right), \mathcal{T}\left(y_1\right) \right), ... \right\}\right)\right)$$
